Accuracy of zero heat flux temperature measurements

### 2019-08-23 meta-analysis.Rmd
navy shinydashboard

data_core <- data %>% #need to adjust for Eshragi, want overall only
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac")

data_core_lowrisk <- data_core %>% # need to adjust for eshragi, want overall only
  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low" & (comments != "Intraoperative, off cardiopulmonary bypass" | comments != "Postoperative"))

data_core_op <- data_core %>% 
  filter(clinical_setting=="Intraoperative" & (clinical_setting != "Postoperative" | clinical_setting != "Intra- and Postoperative"))

data_core_icu <- data_core %>% 
  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

@@

```{r}
out <- loa_maker(data_core_lowrisk$bias,data_core_lowrisk$V_bias,data_core_lowrisk$logs2,data_core_lowrisk$V_logs2)
out <- round(out, digits=3) 
out <- append(out, sum(data_core_lowrisk$n_count, na.rm=T))
out <- append(out, sum(data_core_lowrisk$N, na.rm = T))
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
out[1:12]
```
```{r}
out <- loa_maker(data_core_op$bias,data_core_op$V_bias,data_core_op$logs2,data_core_op$V_logs2)
out <- round(out, digits=3) 
out <- append(out, sum(data_core_op$n_count, na.rm=T))
out <- append(out, sum(data_core_op$N, na.rm = T))
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
out[1:12]
```
```{r}
out <- loa_maker(data_core_icu$bias,data_core_icu$V_bias,data_core_icu$logs2,data_core_icu$V_logs2)
out <- round(out, digits=3) 
out <- append(out, sum(data_core_icu$n_count, na.rm=T))
out <- append(out, sum(data_core_icu$N, na.rm = T))
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
out[1:12]
```

>>>>

data_core <- data %>% #eshragi overall
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

data_core_lowrisk <- data_core %>% #eshragi overall
  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")

data_core_op <- data%>% #eshragi intraop
    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter (clinical_setting=="Intraoperative")

data_core_icu <- data %>% #eshragi postop
      filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

@@

```{r}
out <- loa_maker(data_core_lowrisk$bias,data_core_lowrisk$V_bias,data_core_lowrisk$logs2,data_core_lowrisk$V_logs2)
out <- round(out, digits=3) 
out <- append(out, sum(data_core_lowrisk$n_count, na.rm=T))
out <- append(out, sum(data_core_lowrisk$N, na.rm = T))
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
out[1:12]
```
```{r}
out <- loa_maker(data_core_op$bias,data_core_op$V_bias,data_core_op$logs2,data_core_op$V_logs2)
out <- round(out, digits=3) 
out <- append(out, sum(data_core_op$n_count, na.rm=T))
out <- append(out, sum(data_core_op$N, na.rm = T))
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
out[1:12]
```
```{r}
out <- loa_maker(data_core_icu$bias,data_core_icu$V_bias,data_core_icu$logs2,data_core_icu$V_logs2)
out <- round(out, digits=3) 
out <- append(out, sum(data_core_icu$n_count, na.rm=T))
out <- append(out, sum(data_core_icu$N, na.rm = T))
names(out) <- c("studies","bias","sd","tau2","LOA_L","LOA_U","CI_Lm","CI_Um","CI_Lr","CI_Ur", "n", "N")
out[1:12]
```
,#end fluid Row
            column(12,
                   htmlOutput("selected_subset"),
                   DT::dataTableOutput("summary"))),
